mixchar

### 2018-08-15 README.Rmd
ensure badges all appear right placement

[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)

[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)

@@

Below we will show a basic implementation of the package. For a detailed discussion of the methodology, please see the [website](http://smwindecker.github.io/mixchar/articles/Background.html). You can also find a full worked example on the [website](http://smwindecker.github.io/mixchar/articles/mixchar.html).

>>>>

[![Build Status](https://travis-ci.com/smwindecker/mixchar.svg?branch=master)](https://travis-ci.org/smwindecker/mixchar)
[![codecov](https://codecov.io/gh/smwindecker/mixchar/branch/master/graph/badge.svg)](https://codecov.io/gh/smwindecker/mixchar)
[![repo status](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
[![DOI](https://zenodo.org/badge/103010631.svg)](https://zenodo.org/badge/latestdoi/103010631)

@@

Below we will show a basic implementation of the package. For a detailed step by step workflow, see the [workflow vignette on the website](http://smwindecker.github.io/mixchar/articles/mixchar.html).

For a detailed discussion of the methodology, please see the [methodology vignette on the website](http://smwindecker.github.io/mixchar/articles/Background.html).
